\huge A Usability Evaluation of Tor Launcher

### 2016-11-04 pets2017-paper/pets2017-paper.tex
reword abstract.

  \begin{abstract}
{
{\color {blue}
We evaluate, design, and test the Tor Launcher interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interface interactions.
A 16-participant qualitative study examines user assumptions and common mistakes.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative study shows that our design changes result in
a significant reduction in time. We conclude with recommendations for changes 
to the current interface as well as alternative solutions.
}
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

>>>>

  \begin{abstract}
{
We perform the first usability test on Tor Launcher, a graphical user interface (GUI) 
that all Tor Browser users must use to configure their initial connection to the Tor network. 
We believe that the interface is usable if a new user can to identify what to do,
knows if and when they do the right thing in the process, 
and configures the necessary network components to connect to Tor. 
We use a combination of user observations and user interaction logs to determine
where the interface is not usable, and quantify how unusable the interface is. We 
offer some suggestions for the interface based on what 
we have learned and also suggest alternative approaches 
to bootstrap a connection to Tor that do not require new users to configure the network components. 
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}
